---
title: "Eastern quoll behaviour and dispersal"
author: "Christina Gee, Belinda Wilson"
date: "14 March 2024"
output:
  html_document:
    toc: true
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: true
    theme: cerulean
    highlight: pygments
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'tutorial.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE)
```

# * Background

Personality can play a crucial role in the survival and dispersal of reintroduced animals. In 2017, we reintroduced a cohort of female-only eastern quolls (*Dasyurus viverrinus*) to a [conservation-fenced haven](https://www.mulligansflat.org.au/) in the Australian Capital Territory, and conducted behavioural assays on each animal prior to their release. We aimed to determine whether personality and plasticity of these animals could predict their post-release performance.

Here we describe the analyses we conducted for our article [Wilson *et al.* (2022) Personality and plasticity predicts post-release performance in a reintroduced mesopredator](https://doi.org/10.1016/j.anbehav.2022.02.019), published in Animal Behaviour.

# * Setup

First, we installed the [pacman Package Management Tool](https://cran.r-project.org/web/packages/pacman/index.html), which allows us to install and load subsequent packages in a condensed and efficient way. 

```{r, eval=FALSE}
#install.packages("pacman")
```

```{r, results='hide', warning=FALSE, message=FALSE}
# Install and load required packages
pacman::p_load(basemaps, ggplot2, ggpubr, gtools, janitor, lme4,lmerTest, MuMIn,  
               readr, sf, readxl, rstudioapi, tidyverse, viridis, beepr, corrplot,
               broom, sjPlot, sjmisc, sjlabelled)


install.packages("knitr")

library("knitr")

```

# *Data preparation

```{r, eval=FALSE}
# Assign raw data filename to an object
raw_data <- "data.xlsx"

# Read in behavioural assay data
raw <- read_excel(raw_data, sheet="Assays", na="N/A") %>% 
  clean_names() %>%
  select("id"="observation_id", 
         "assay_id", 
         "quoll_code",
         behaviour="behavior", 
         occurrences="total_number_of_occurences")

#view(raw)


#Read in the data for all data sheets in excel 
meta <- read_excel(raw_data, sheet="Metadata", na="N/A") %>% 
  select(-16, -17) %>%
  clean_names()
#view(meta)
#names(meta)

quoll <- read_excel(raw_data, sheet="Quoll", na="N/A") %>%
  select(2, 4, 5) %>%
  clean_names()
#view(quoll)
#names(quoll)

capture <- read_excel(raw_data, sheet="Captures") %>%
   select(2, 4, 8, 9, 10, 11, 12, 13, 14, 24, 26, 27, 28, 30) %>%
  clean_names()
#view(capture)
#names(capture)

session <- read_excel(raw_data, sheet="Sessions") %>%
  select(4, 8, 9, 10, 11) %>%
  clean_names()
#view(session)
#names(session)

#bin <- read_excel(raw_data, sheet="Binned assays", na="N/A")%>%
 # clean_names()
#view(bin)

#sites <- read_excel(raw_data, sheet="Sites") %>%
  #clean_names()
#view(sites)

#trap_eff <- read_excel(raw_data, sheet="Trap effectiveness") %>%
 #clean_names()
#view(trap_eff)


#Clean up behaviour data from long to wide format 
occ <- pivot_wider(data = raw, 
                   names_from = behaviour, 
                   values_from = occurrences)  %>%
  clean_names() %>%
  mutate(across(all_of(c("section_1", "section_2", "section_3", "section_4", 
                         "moving", "jump_climb", "food", "legs", 
                         "grooming", "resting", "perch")), as.numeric)) %>%
  rename(section_1_o = "section_1", 
         section_2_o = "section_2", 
         section_3_o = "section_3", 
         section_4_o = "section_4", 
         moving_o = "moving", 
         jump_climb_o = "jump_climb", 
         food_o = "food", 
         legs_o = "legs", 
         grooming_o = "grooming", 
         resting_o = "resting", 
         perch_o = "perch")
#view(occ)


raw <- read_excel(raw_data, sheet="Assays", , na="N/A") %>% 
  clean_names() %>%
  select("id"="observation_id", 
         "assay_id", 
         quoll_code, 
         behaviour="behavior", 
         duration="total_duration_s")

dur <- pivot_wider(data = raw,
                   names_from = behaviour, 
                   values_from = duration) %>%
  clean_names() %>%
  mutate(across(all_of(c("section_1", "section_2", "section_3", "section_4", 
                         "moving", "jump_climb", "food", "legs", 
                         "grooming", "resting", "perch")), as.numeric)) %>%
  rename(section_1_d = "section_1", 
         section_2_d = "section_2", 
         section_3_d = "section_3", 
         section_4_d = "section_4", 
         moving_d = "moving", 
         jump_climb_d = "jump_climb", 
         food_d = "food", 
         legs_d = "legs", 
         grooming_d = "grooming", 
         resting_d = "resting", 
         perch_d = "perch")
#view(dur)

assays <- left_join(occ, dur, by=c("id", "assay_id", "quoll_code"))

#Adding all sections together to create a column with total section visitations
assays$sumsect_o <- rowSums(assays[, c("section_1_o", "section_2_o", "section_3_o", "section_4_o")])

#Finding out the locations of the relevant columns 
colfoodo <- which(colnames(assays) == "food_o")
print(colfoodo) #4

restingo <- which(colnames(assays) == "resting_o")
print(restingo) #10

#Adding together all activity occurrences without sections
assays$totalact_o <- rowSums(assays[, c(4:10)])

#view(assays)

# Append metadata for each assay to dataframe
data <- left_join(meta, assays, by=c("assay_id", "quoll_code"))
#view(data)

#this filters out animals which were not assayed
data <- data %>%
  filter(!is.na(assay_number))

data <- left_join(data, quoll, by=c("quoll_code"), relationship = "many-to-many")

data <- left_join(data, capture, by=c("quoll_code", "session"), relationship = "many-to-many")

data <- left_join(data, session, by=c("session"))

view(data)

```

# * Calculating time differences 
```{r}

#Check if the time columns are in the correct format
print(class(data$snout_in_arena))

#If not, correct to POSIXct format
data$snout_in_arena <- as.POSIXct(data$snout_in_arena)
data$process_end <- as.POSIXct(data$process_end)
data$first_light <- as.POSIXct(data$first_light)

#Calculate time differences
data$time_processtoassay <- data$snout_in_arena - data$process_end
data$time_assaytolight <- data$snout_in_arena - data$first_light

#view(data)

```

# * Extracting 1st assay data for 'personality' / 'tendency' analysis
```{r}

data1 <- data %>%
    filter(assay_number !=2)

view(data1)

```

# * Filtering out the two individuals who were assayed in Sept 2023
```{r}
data1_excl <- data1 %>%
  filter(!(quoll_code %in% c("53328", "87DE0")))

view(data1_excl)

```

# * Testing environmental variables for influence on behaviour 
```{r}

foodd <- glm(food_d ~ temp + moon_phase + time_assaytolight, data=data1)
foodo <- glm(food_o ~ temp + moon_phase + time_assaytolight, data=data1)

groomd <- glm(grooming_d ~ temp + moon_phase + time_assaytolight, data=data1)
groomo <- glm(grooming_o ~ temp + moon_phase + time_assaytolight, data=data1)

jumpd <- glm(jump_climb_d ~ temp + moon_phase + time_assaytolight, data=data1)
jumpo <- glm(jump_climb_o ~ temp + moon_phase + time_assaytolight, data=data1)

legsd <- glm(legs_d ~ temp + moon_phase + time_assaytolight, data=data1)
legso <- glm(legs_o ~ temp + moon_phase + time_assaytolight, data=data1)

moved <- glm(moving_d ~ temp + moon_phase + time_assaytolight, data=data1)
moveo <- glm(moving_o ~ temp + moon_phase + time_assaytolight, data=data1)

perchd <- glm(perch_d ~ temp + moon_phase + time_assaytolight, data=data1)
percho <- glm(perch_o ~ temp + moon_phase + time_assaytolight, data=data1)

restd <- glm(resting_d ~ temp + moon_phase + time_assaytolight, data=data1)
resto <- glm(resting_o ~ temp + moon_phase + time_assaytolight, data=data1)

bait <- glm(remaining_bait_g ~ temp + moon_phase + time_assaytolight, data=data1)

```

# * Collect evironmental  stats into a table
```{r}

p_temp <- summary(foodd)$coefficients["temp", "Pr(>|t|)"]
p_moon <- summary(foodo)$coefficients["moon_phase", "Pr(>|t|)"]

data.frame(Model = c("foodd", "foodo"),
           Variable = c("Temperature", "Moon phase"),
           p_value = c(p_temp, p_moon))


tidy_results <- bind_rows(tidy(bait))

print(tidy_results)

tab_model(
  restd, 
  resto, 
  pred.labels = c("Intercept", "Temperature", "Moon phase", "Time to first light"),
  dv.labels = c("
                Resting duration (s)", "
                Resting occurrences (n)"),
  string.pred = "Coefficient",
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value"
)


tab_model(
  bait, 
  pred.labels = c("Intercept", "Temperature", "Moon phase", "Time to first light"),
  dv.labels = c("
                Remaining bait (g)"),
  string.pred = "Coefficient",
  string.ci = "Conf. Int (95%)",
  string.p = "P-Value"
)

```

# * Accounting for environmental variables
```{r}

#Mutating the environmental variables in the 1st assay df, including animals 53328 and 87DE0
names(data1)

data1_mutate <- data1 %>%
  mutate_at(vars(5, 56, 61), ~ as.vector(scale(.)))

view(data1_mutate)

write.csv(data1_mutate, "data 1st assay mutated.csv")


#Mutating environmental variables excluding 53328 and 87DE0
names(data1_excl)

data1ex_mutate <- data1_excl %>%
  mutate_at(vars(5, 56, 61), ~ as.vector(scale(.)))

write.csv(data1ex_mutate, "data 1st assay mutated exl Sept individuals.csv")

```

# * Correlation analysis
```{r}

#Finding out the locations of the relevant columns 
colfoodo <- which(colnames(megadata) == "food_o")
print(colfoodo) #22
restingo <- which(colnames(megadata) == "resting_o")
print(restingo) #28
colsection4o <- which(colnames(megadata) == "section_4_o")
print(colsection4o) #32
colfoodd <- which(colnames(megadata) == "food_d")
print(colfoodd) #33
restingd <- which(colnames(megadata) == "resting_d")
print(restingd) #39
colsection4d <- which(colnames(megadata) == "section_4_d")
print(colsection4d) #43

#Selecting the appropriate columns for each correlation matrix
#all occurrence and duration columns including sections
cor_o_d <- megadata %>% 
  dplyr::select(22:43)

#all occurrence columns including sections
cor_o <- megadata %>%
  dplyr::select(22:32)

#all duration data including sections 
cor_d <- megadata %>%
  dplyr::select(33:43)

#all duration and occurrence data not including sections
cor_od_act <- megadata %>%
  dplyr::select(22:28, 33:39)

#all occurrence data not including sections
cor_o_act <- megadata %>%
  dplyr::select(22:28)

#all duration data not including sections
cor_d_act <- megadata %>%
  dplyr::select(33:39)

#Running the correlations tests for both, then occurrences, then duration, with sections
correlation_od <- cor(cor_o_d)
correlation_o <- cor(cor_o)
correlation_d <- cor(cor_d)

#Running the correlations for both, then occurrences v duration, then occurrences, then duration, without sections
correlation_od_act <- cor(cor_od_act)
correlation_ovd_act <- cor(cor_d_act,cor_o_act)
correlation_occ_act <- cor(cor_o_act)
correlation_dur_act <- cor(cor_d_act)

#Saving them to a .csv file
write.csv(correlation_od, "correlation matrix occ dur all sessions.csv")
write.csv(correlation_o, "correlation matrix occ all sessions.csv")
write.csv(correlation_d, "correlation matrix dur all sessions.csv")
write.csv(correlation_ovd_act, "correlation matrix activity occ vs dur all sessions.csv")
write.csv(correlation_occ_act, "correlation matrix activity occ all sessions.csv")
write.csv(correlation_dur_act, "correlation matrix activity dur all sessions.csv")

#Creating and printing correlation matrix .jpgs which colour code the correlations

#Correlation of occurrences and duration with sections
jpeg(height=2000, width=2000, file="correlation matrix od all sessions.jpeg", type="cairo")
corrplot(correlation_od, method="color", type="upper", #creates a correlation matrix
         cl.cex=3, number.cex=2, tl.cex=3, diag=FALSE,
         tl.col="black", tl.srt=45, addCoef.col="black")
dev.off()

#Correlations of duration and occurrences without sections
jpeg(height=2000, width=2000, file="correlation matrix occdur act all sessions.jpeg", type="cairo")
corrplot(correlation_od_act, method="color", type="upper", #creates a correlation matrix
         cl.cex=3, number.cex=2, tl.cex=3, diag=FALSE,
         tl.col="black", tl.srt=45, addCoef.col="black")
dev.off()

```

# * Running basic models to get the feel of the data
```{r}

#GLM to test duration of moving, first with all individuals, and then excluding the Sept 2023 individuals 
summary(glm(moving_d ~ study_site + temp + assay_number + morph + sex +  age_estimate, data=megadata))
summary(glm(moving_d ~ study_site + temp + assay_number + morph + sex +  age_estimate, data=megadata_excl))

```

#Step 1 extract predicted values for behaviour with environmental variables
```{r}

mod <- glm(food_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$foodo_pred <- predict(mod, type = "response")
mod <- glm(food_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$foodd_pred <- predict(mod, type = "response")
             
mod <- glm(grooming_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$groomo_pred <- predict(mod, type = "response")
mod <- glm(grooming_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$groomd_pred <- predict(mod, type = "response")
             
mod <- glm(jump_climb_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$jumpo_pred <- predict(mod, type = "response")
mod <- glm(jump_climb_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$jumpd_pred <- predict(mod, type = "response")

mod <- glm(legs_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$legsd_pred <- predict(mod, type = "response")
mod <- glm(legs_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$legso_pred <- predict(mod, type = "response")

mod <- glm(moving_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$moved_pred <- predict(mod, type = "response")
mod <- glm(moving_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$moveo_pred <- predict(mod, type = "response")

mod <- glm(perch_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$perchd_pred <- predict(mod, type = "response")
mod <- glm(perch_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$percho_pred <- predict(mod, type = "response")

mod <- glm(resting_d ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$restd_pred <- predict(mod, type = "response")
mod <- glm(resting_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$resto_pred <- predict(mod, type = "response")

mod <- glm(remaining_bait_g ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=
             data1_mutate)
             data1_mutate$bait_pred <- predict(mod, type = "response")
             
view(data1_mutate)
names(data1_mutate)

```

# * Creating df that is predicted variables accounting for environmental heterogeneity
```{r}

data1_pred <- data1_mutate %>%
              select(-food_o, -food_d, -grooming_o, -grooming_d, -jump_climb_o, -jump_climb_d,
                     -legs_o, -legs_d, -moving_o, -moving_d, -perch_d, -perch_o, -resting_o,
                     -resting_d, -remaining_bait_g)

view(data1_pred)
names(data1_pred)

```

Now we have our predicted values, accounting for environmental heterogeneity. 

#Step 2 Analyse behaviour indicators (name?)

  1. Test the influence of fixed (e.g., site) and random effects (e.g., arena) on behavioural responses (e.g., food interaction duration) using the `lmer()` function.
  2. If multiple fixed effects produce significance, perform model selection using the dredge() function to determine which fixed effects are within delta 2 AICc.

*Personality (single response / static etc? figure this out)*

```{r}

names(data1_pred)

# Test random effects using LMER 
mod1 <- lmer(bait_pred ~ study_site + sex + age_estimate + condition + 
              body_weight_kg + morph + (1|quoll_code) + (1|arena), 
            data=data1_pred, na.action = "na.fail")

mod2 <- lmer(foodd_pred ~ study_site + sex + age_estimate + condition + 
              body_weight_kg + morph + (1|quoll_code) + (1|arena), 
            data=data1_pred, na.action = "na.fail")

# Display summary statistics
summary(mod1)
summary(mod2)

# Display model selection table for fixed effects
dredge(mod1, rank = "AICc")

# Preliminary plot
ggplot(data=data1_pred, aes(x=study_site, y=bait_pred, fill=study_site)) +
  geom_boxplot()
```

# * Collect LMER stats into a table
```{r}

tidy_results <- bind_rows(tidy(bait))
print(tidy_results)

tab_model(mod1)

tab_model(
  mod1,
  show.se = TRUE,
  pred.labels = c("Intercept", "Study site (MFWS)", "Sex (M)", "Age estimate 1-2yrs", "Age estimate 2-3yrs", "Body condition (Fair)", "Body condition (Good)", "Weight (kg)", "Morph (Fawn)"),
  dv.labels = c("Bait remaining (g)"),
  string.pred = "Estimates",
  string.ci = "Conf. Int (95%)",
  string.stat = "T-value",
  string.p = "P-Value"
)

```

# * Plots of demographic fixed variables
```{r}

#Belinda's  Preliminary plot
ggplot(data=data1_pred, aes(x=study_site, y=bait_pred, fill=study_site)) +
  geom_boxplot()

perch_plot <- ggplot(data=data1_pred, aes(x = sex, y = percho_pred, 
                        fill = sex)) + 
  geom_boxplot() +
  scale_fill_manual (values = c("#25798F","#7BD151")) +
  #facet_wrap(~study_site) + 
  theme_minimal() +
  theme(legend.position = "none", 
        panel.grid = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black")) + 
  xlab("Sex") + ylab("Perching occurrences (n)") + labs("")

print(perch_plot)


move_plot <- ggplot(data=data1_pred, aes(x = study_site, y = moveo_pred, 
                        fill = study_site)) + 
  geom_boxplot() +
  scale_fill_manual (values = c("#25798F","#7BD151")) +
  #facet_wrap(~study_site) + 
  theme_minimal() +
  theme(legend.position = "none", 
        panel.grid = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black")) + 
  xlab("Study site") + ylab("Quadrupedal movement occurrences (n)") + labs("")


print(bait_plot)

bait_plot <- ggplot(data=data1_pred, aes(x = study_site, y = bait_pred, 
                        fill = study_site)) + 
  geom_boxplot() +
  scale_fill_manual (values = c("#25798F","#7BD151")) +
  #facet_wrap(~study_site) + 
  theme_minimal() +
  theme(legend.position = "none", 
        panel.grid = element_blank(),
        axis.line.x = element_line(color = "black"),
        axis.line.y = element_line(color = "black")) + 
  xlab("Study site") + ylab("Amount of bait not eaten (g)") + labs("")

```

# Collecting statistics for a model table (🚩 this goes at the end of your independent variable modelling).
```{r}
# Generate a model
mod <- glm(food_o ~ temp + moon_phase + time_assaytolight, 
           family=gaussian, data=megadata_mutate, 
           na.action = "na.fail")

summary(mod)

#collect stats into a table
p_temp <- summary(mod)$coefficients["temp", "Pr(>|t|)"]
p_moon <- summary(mod)$coefficients["moon_phase", "Pr(>|t|)"]

data.frame(Variable = c("Temperature", "Moon phase"),
           p_value = c(p_temp, p_moon))

# Conduct model selection using AICc threshold
dredge(mod, rank = "AICc")


```


#Step 3 Run GLMs for assay numbers and if this is significant, do step 3b in mind map plan
```{r}

mod_fo_p <- glm(mod_fo_p ~ assay_number, family=gaussian, data=megadata_mutate)
mod_fd_p <- glm(mod_fd_p ~ assay_number, family=gaussian, data=megadata_mutate)

```


## Map
```{r, warning=FALSE}
# Read in and project MFWS fence shapefile using rgdal
mfws <- readOGR(dsn="shapefiles/MFGO_fences_and surrounds.shp", verbose=FALSE) %>% 
  spTransform(CRS("+proj=utm +zone=55 +ellps=WGS84")) %>%
  # Transform shapefile into a dataframe
  fortify(verbose=FALSE) %>%
  mutate(lat=as.numeric(lat + 10000000), 
         long=as.numeric(long))

# Read in and project MFGO fence shapefile using rgdal
mfgo <- st_read("shapefiles/MFGO_fences.shp", quiet=TRUE) %>%
  # Set projection to eastings/northings
  st_set_crs("EPSG:32755") %>% 
  # Reproject to lat/long
  st_transform("EPSG:4326")

# Plot den locations on MFWS map for each trial
map <- ggplot() + 
  geom_polygon(mfws, mapping=aes(x=long, y=lat, group=group), col="grey15") +
  #coord_sf(xlim=c(695750, 699250), ylim=c(6104250, 6107750)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_rect(fill="white"),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        legend.key = element_blank(), 
        strip.background = element_blank()) +
  #facet_wrap(~factor(year_of_acquisition), ncol=3) +
  #scale_colour_manual(values = viridis(3, begin=0.9, end=0.1)) +
  xlab("") + ylab("") + labs(col="Trial")
print(map)
```

```{r}
jpeg(file="mfgo_fences_and_surrounds.jpeg", 
     width=4750, height=1500, units="px", res=500)
map
dev.off()
```

# **Session information**
```{r}
# Display version information for R, OS, and packages
sessionInfo()
```