---
title: "Eastern quoll behaviour and dispersal"
author: "Christina Gee, Belinda Wilson"
date: "3 August 2023"
output:
  html_document:
    toc: true
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: true
    theme: cerulean
    highlight: pygments
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), 'tutorial.html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=TRUE)
```

# **Background**

Personality can play a crucial role in the survival and dispersal of reintroduced animals. In 2017, we reintroduced a cohort of female-only eastern quolls (*Dasyurus viverrinus*) to a [conservation-fenced haven](https://www.mulligansflat.org.au/) in the Australian Capital Territory, and conducted behavioural assays on each animal prior to their release. We aimed to determine whether personality and plasticity of these animals could predict their post-release performance.

Here we describe the analyses we conducted for our article [Wilson *et al.* (2022) Personality and plasticity predicts post-release performance in a reintroduced mesopredator](https://doi.org/10.1016/j.anbehav.2022.02.019), published in Animal Behaviour.

# **Setup**

First, we installed the [pacman Package Management Tool](https://cran.r-project.org/web/packages/pacman/index.html), which allows us to install and load subsequent packages in a condensed and efficient way. 

```{r, eval=FALSE}
#install.packages("pacman")
```

```{r, results='hide', warning=FALSE, message=FALSE}
# Install and load required packages
pacman::p_load(basemaps, ggplot2, ggpubr, gtools, janitor, lme4, rgdal, 
               readr, sf, readxl, rstudioapi, tidyverse, viridis)
```

We also set the working directly to where this R markdown is saved using the `rstudioapi` package.

```{r}
# Set the working directory to where this markdown is saved
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

# **Data preparation**

```{r, eval=FALSE}
# Assign raw data filename to an object
raw_data <- "data.xlsx"

# Read in den location data
data <- read_excel(raw_data, sheet="data") %>% 
  clean_names() 
```

## Map

```{r, warning=FALSE}
# Read in and project MFWS fence shapefile using rgdal
mfws <- readOGR(dsn="shapefiles/MFGO_fences_and surrounds.shp", verbose=FALSE) %>% 
  spTransform(CRS("+proj=utm +zone=55 +ellps=WGS84")) %>%
  # Transform shapefile into a dataframe
  fortify(verbose=FALSE) %>%
  mutate(lat=as.numeric(lat + 10000000), 
         long=as.numeric(long))

# Read in and project MFGO fence shapefile using rgdal
mfgo <- st_read("shapefiles/MFGO_fences.shp", quiet=TRUE) %>%
  # Set projection to eastings/northings
  st_set_crs("EPSG:32755") %>% 
  # Reproject to lat/long
  st_transform("EPSG:4326")

# Plot den locations on MFWS map for each trial
map <- ggplot() + 
  geom_polygon(mfws, mapping=aes(x=long, y=lat, group=group), col="grey15") +
  #coord_sf(xlim=c(695750, 699250), ylim=c(6104250, 6107750)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_rect(fill="white"),
        axis.text.x = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        legend.key = element_blank(), 
        strip.background = element_blank()) +
  #facet_wrap(~factor(year_of_acquisition), ncol=3) +
  #scale_colour_manual(values = viridis(3, begin=0.9, end=0.1)) +
  xlab("") + ylab("") + labs(col="Trial")
print(map)
```

```{r}
jpeg(file="mfgo_fences_and_surrounds.jpeg", 
     width=4750, height=1500, units="px", res=500)
map
dev.off()
```

# **Analysis**

```{r}

```

# **Plots**

```{r}

```

# **Session information**

```{r}
# Display version information for R, OS, and packages
sessionInfo()
```